---
title: "Project description"
callout-icon: false
editor: visual
---

# Descriptive Statistics {#descriptives}

Please put your work for component 2, descriptive statistics, in this document.

```{r setup}
library(tidyverse)
library(openintro)
```

### Part 1: Understanding your variables

-   Write down your research question (from component 1)

-   Write down your hypothesis (from component 1)

-   Write down the name of your data set (from component 1)

-   Write down the names of the variables you will use in your analysis (i.e., what you need to type to access them in R)

-   For each variable, write:

    -   A brief description of what it measures

    -   Whether it is an explanatory (independent) variable, a response (dependent) variable, or something else (explain what)

    -   What kind of variable it is (categorical or numeric and which subtype within these)


### Part 2: Univariate distributions

-   For each of your variables:

    -   Look at its distribution using the summary() or table() function (as appropriate to its type). 
    -   Indicate how many missing values (NAs) there are.
    -   In ~2-3 sentences, describe what you see in the results. Note anything that surprises you.

```{r}
# replace the contents of this code chunk with tables/summaries of your variables (you can copy and paste the chunk to display different variables separately)
summary(lizard_run$top_speed)
table(lizard_run$common_name, useNA = "always")
```


### Part 3: Preparing your data set

-   Will you analyze all the observations in your data set? Explain why or why not. If not, which will you include and which will you exclude?

-   Do you need to create any new variables? Explain why or why not. If so, what are they?

-   If necessary, use the code chunk below to make any needed changes (filtering observations and creating variables) to your data. Check whether they worked as expected.

```{r}
lizardhabitats_filtered <- filter(lizard_habitat, site == "desert")

lizardhabitats_newvars <- mutate(lizardhabitats_filtered, anysun = sunlight != "shade")

table(lizardhabitats_newvars$site, useNA = "always")
table(lizardhabitats_newvars$sunlight, lizardhabitats_newvars$anysun)
```

### Part 4: Multivariate visualizations

-   Make a plot showing the relationship between your explanatory (independent) and response (dependent) variables.
    Depending on your variable types, this might be a scatter plot, box plot, bar chart, etc.
    Include meaningful axis labels.

-   Interpret your plot in a few sentences.
    Does it appear these variables are associated with one another?
    Does anything about the relationship surprise you?
    Is it consistent or inconsistent with your hypothesis?

```{r}
# replace the contents of this chunk with code to create your plot
ggplot(lizard_run, aes(x = top_speed, y = common_name)) + 
  geom_boxplot() + 
  labs(x = "Top running speed (meters per second)", 
       y = "Species",
       title = "Top speeds of two species of cool lizards")
```